\bf Faster Neural Machine Translation Inference

### 2018-01-24 fast-beam/fast-beam.tex
fast nmt paper

\documentclass[]{article}
\usepackage[letterpaper]{geometry}
\usepackage{amta2016}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{natbib}
\usepackage{layout}
\usepackage{algorithmic}
\usepackage{graphicx}

@@

\begin{figure} [h]
\begin{algorithmic}
\WHILE{more input} 
  \STATE Create encoding batch
\ENDWHILE 
\end{algorithmic}
\caption{Add Bias Term}
\label{algo:Add Bias Term}
\end{figure}

\begin{figure} [h]
\begin{algorithmic}
\WHILE{more input} 
  \STATE Create encoding batch
\ENDWHILE 
\end{algorithmic}
\caption{Calculate softmax}
\label{algo:Calculate softmax}
\end{figure}

\begin{figure} [h]
\begin{algorithmic}
\WHILE{more input} 
  \STATE Create encoding batch
\ENDWHILE 
\end{algorithmic}
\caption{Find best}
\label{algo:Find best}
\end{figure}

@@

Thirdly, we are only interested in the probability of the best class. Since we have precalculated the best class in Figure~\ref{algo:Calculate softmax}, we shall only calculate softmax for this one class, avoiding the computational and memory bandwith of computing the probability for all classes.

In fact, we are usually only interested in the argmax class during inference, not the probability. Therefore, by using the argmax calculated in Figure~\ref{algo:Calculate softmax}, we can avoid computing the softmax altogether. The outline of the our function is shown in Figure~\ref{algo:Fused Kernel}.

\begin{figure} [h]
\begin{algorithmic}
\WHILE{more input} 
  \STATE Create encoding batch
\ENDWHILE 
\end{algorithmic}
\caption{Fused Kernel}
\label{algo:Fused Kernel}
\end{figure}

@@

>>>>

\documentclass[]{article}
\usepackage[letterpaper]{geometry}
\usepackage{amta2016}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{natbib}
\usepackage{layout}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}

@@

\begin{figure} [h]
\begin{algorithmic}
\REQUIRE activation vector $p$, bias vector $b$
\FORALL{$p_i$ in $p$}
  \STATE $p_i \gets p_i + b_i$
\ENDFOR 
\end{algorithmic}
\caption{Add Bias Term}
\label{algo:Add Bias Term}
\end{figure}

\begin{figure} [h]
\begin{algorithmic}
\REQUIRE activation vector $p$

\COMMENT{calculate max for softmax stability}

\STATE $max \gets - \infty$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i > max$}
    \STATE $max \gets p_i$
  \ENDIF
\ENDFOR

\COMMENT{calculate denominator}

\STATE $sum \gets 0$ 
\FORALL{$p_i$ in $p$}
  \STATE $sum \gets sum + e^{p_i}$
\ENDFOR

\COMMENT{calculate softmax}

\FORALL{$p_i$ in $p$}
  \STATE $p_i \gets \frac{e^{p_i}}{sum} $
\ENDFOR

\RETURN $p$

\end{algorithmic}
\caption{Calculate softmax}
\label{algo:Calculate softmax}
\end{figure}

\begin{figure} [h]
\begin{algorithmic}
\REQUIRE softmax vector $p$

\STATE $max \gets - \infty$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i > max$}
    \STATE $max \gets p_i$
    \STATE $argmax \gets i$
  \ENDIF
\ENDFOR

\RETURN $max$, $argmax$

\end{algorithmic}
\caption{Find best}
\label{algo:Find best}
\end{figure}

@@

Thirdly, we are only interested in the probability of the best class. Since we have precalculated the best class in Figure~\ref{algo:Calculate softmax}, we shall only calculate softmax for this one class, avoiding the computational and memory bandwith of computing the probability for all classes. The outline of the our function is shown in Figure~\ref{algo:Fused Kernel}.

In fact, we are usually only interested in the argmax class during inference, not the probability. Therefore, we can skip the second iteration over $p$ in Figure~\ref{algo:Fused Kernel} and avoid computing the softmax altogether.

\begin{figure} [h]
\begin{algorithmic}
\REQUIRE activation vector $p$, bias vector $b$

\COMMENT{add bias, calculate $max$ \& $argmax$}

\STATE $max \gets - \infty$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i + b_i > max$}
    \STATE $max \gets p_i + b_i$
    \STATE $argmax \gets i$
  \ENDIF
\ENDFOR

\COMMENT{calculate denominator}

\STATE $sum \gets 0$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i > max$}
    \STATE $sum \gets sum + e^{p_i - max}$
  \ENDIF
\ENDFOR

\COMMENT{calculate softmax($p_i$)}
\RETURN $\frac{e^{max}}{sum}$, $argmax$

\end{algorithmic}
\caption{Fused Kernel}
\label{algo:Fused Kernel}
\end{figure}

@@

We trained a sequence-to-sequence, encoder-decoder NMT system similar to that described in (Rico ???). This uses recurrent neural network with gated recurrent units. The input and output vocabulary size were both set to 85,000 using BPE ??? to adjust the vocabulary to the desired size. The hidden layer dimensions were kept at the default of 512. We used the Marian toolkit to train our models.

For inference, we used Amun (???), the current fastest open-source inference engine for the RNN/GRU model we aware of.

Our training data consisted of the German-English parallel sentences from the Europarl corpus (???). To test inference speed, we used two test set with differing characteristics:
\begin{enumerate}
   \item \vspace{-2 mm} a subset of the training data, which contains mostly long sentences, and is, of course, in the same domain as the training data
   \item \vspace{-2 mm} a subset of the German-English data from the Open-Subtitles corpus, consisting of mostly short, out-of-domain sentences.
\end{enumerate}
Table~\ref{tab:corpora} gives details of the training and test corpora.

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		& ar-en		& fr-en \\ \hline
\multicolumn{3}{|l|}{For speed testing} \\ \hline
Set name	& \multicolumn{2}{|c|}{Subset of training data} \\
\# sentences  	& 800k 		& 200k \\
\# words 	& 5.8m 		& 5.9m \\ 
Avg words/sent	& 7.3		& 29.7 \\ \hline
\multicolumn{3}{|l|}{For model score testing} \\ \hline
Set name	& OpenSubtitles	& newstest2011 \\
\# sentences  	& 2000 		& 3003 \\
\# words 	& 14,620 	& 86,162 \\ 
Avg words/sent	& 7.3		& 28.7 \\ \hline
\end{tabular}
\end{center}
\caption{Corpora}
\label{tab:corpora}
\end{table}
